---
title: "SQMF Formative Assessment FT2"
author: "EXAM NUMBER"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())

# I will attach the packages you need
library(tidyverse)
library(ggeffects)
```

# The data: English visual lexical decision and naming latencies

Read the data `./data/english.csv`.

```{r read}
english <- ...
```

The `english` data set contains mean visual lexical decision latencies `RTlexdec` and word
naming latencies `RTnaming` based on 2284 mono-morphemic English nouns and verbs,
averaged for old and young subjects `AgeSubject`

There are also various predictor variables related to properties of each word.

Here's an explanation of each column in the data set.

- `RTlexdec`: numeric vector of log RT in visual lexical decision.
- `RTnaming`: numeric vector of log RT in word naming.
- `Familiarity`: numeric vector of subjective familiarity ratings.
- `Word`: a factor with 2284 words.
- `AgeSubject`: a factor with as levels the age group of the subject: 
          `young` versus `old`. 
- `WordCategory`: a factor with as levels the word categories 
          `N` (noun) and `V` (verb). 
- `WrittenFrequency`: numeric vector with log frequency in the CELEX lexical
          database. 
- `WrittenSpokenFrequencyRatio`: numeric vector with the logged ratio 
          of written frequency (CELEX) to spoken frequency (British National Corpus). 
- `FamilySize`: numeric vector with log morphological family size. 
- `DerivationalEntropy`: numeric vector with derivational entropy. 
- `InflectionalEntropy`: numeric vector with inflectional entropy. 
- `NumberSimplexSynsets`: numeric vector with the log-transformed count of 
          synonym sets in WordNet in which the word is listed. 
- `NumberComplexSynsets`: numeric vector with the log-transformed count of
          synonym sets in WordNet in which the word is listed as part of a compound. 
- `LengthInLetters`: numeric vector with length of the word in letters. 
- `Ncount`: numeric vector with orthographic neighborhood density, defined as the number of lemmas in CELEX with the same length (in letters) 
    at Hamming distance 1. 
- `MeanBigramFrequency`: numeric vector with mean log bigram frequency. 
- `FrequencyInitialDiphone`: numeric vector with log frequency of initial diphone. 
- `ConspelV`: numeric vector with type count of orthographic neighbors. 
- `ConspelN`: numeric vector with token count of orthographic neighbors. 
- `ConphonV`: numeric vector with type count of phonological neighbors. 
- `ConphonN`: numeric vector with token count of phonological neighbors. 
- `ConfriendsV`: numeric vector with type counts of consistent words. 
- `ConfriendsN`: numeric vector with token counts of consistent words. 
- `ConffV`: numeric vector with type count of forward inconsistent words.
- `ConffN`: numeric vector with token count of forward inconsistent words.
- `ConfbV`: numeric vector with type count of backward inconsistent words. 
- `ConfbN`: numeric vector with token count of backward inconsistent words.
- `NounFrequency`: numeric vector with the frequency of the word used as noun. 
- `VerbFrequency`: numeric vector with the frequency of the word used as verb. 
- `CV`: factor specifying whether the initial phoneme of 
          the word is a consonant (`C`) or a vowel (`V`). 
- `Obstruent`: factor specifying whether the initial phoneme 
          of the word is a continuant (`cont`) or an obstruent (`obst`). 
- `Frication`: factor specifying whether the initial phoneme 
          has a burst (`burst`) or frication (`frication`) for 
          consonant-initial words, and for vowel-initial words whether the vowel is 
          `long` or `short`. 
- `Voice`: factor indicating whether the initial phoneme is `voiced`
          or `voiceless`. 
- `FrequencyInitialDiphoneWord`: numeric vector with the log-transformed 
          frequency of the initial diphone given that it is syllable-initial. 
- `FrequencyInitialDiphoneSyllable`: numeric vector with the log-transformed 
          frequency of the initial diphone given that it is word initial. 
- `CorrectLexdec`: numeric vector with the proportion of 
          subjects that accepted the item as a word in lexical decision.


Balota, D.A., Cortese, M.J. and Pilotti, M. (1999) *Visual lexical decision latencies for 2906 words*. <http://www.artsci.wustl.edu/~dbalota/lexical_decision.html>.

Spieler, D. H. and Balota, D. A. (1998) *Naming latencies for 2820 words*. <http://www.artsci.wustl.edu/~dbalota/naming.html>.

# Modelling reaction times

The following code chunk contains a linear model.

Pick another discrete predictor and another continuous predictor and add them to the model.

```{r eng-lm}
eng_lm <- lm(
  # Replace ... with a discrete and a continuous predictor
  RTlexdec ~ WrittenFrequency + AgeSubject + ... + ...,
  data = english
)

summary(eng_lm)
```

**NOTE**: `RTltxdec` is in logs rather than milliseconds, but how to interpret coefficients does not change (only the measurement unit is different).

Now use `ggpredict()` to calculate the predicted mean log-RT depending on the different predictors.

```{r eng-lm-pred}
ggpredict(eng_lm, ...)
```

And finally, plot the model predictions.

```{r eng-lm-plot}
ggpredict(eng_lm, ...) %>%
  plot()
```

# Reporting

Now write a full report of the model you have run.
Remember that you have to report both the model specifications (outcome, predictors, levels, type of coding for the predictors, ...) and the results.

...

# Render (knit) this report

Now you can render (aka knit) this report.

Just click on the Knit button!

# Submit your assessment on GitHub

When you are done, upload this file and the `analysis.html` file from this RStudio Project to GitHub,
in the repository of the FT2 assessment.
